Block bootstrap consistency\\under weak assumptions

### 2017-03-10 Paper.tex
[#38/ui] replace proof of 'maximal' ui result (Lemma 6)
The old version of the proof of Lemma 6 was incorrect -- there were
insurmountable measurability issues that I'd missed in earlier versions
of the paper. This commit replaces it with a proof based on McLeish's
proof for mixingales.

By construction, (see Equations~\eqref{eq:39} and~\eqref{eq:1})
\begin{equation}\label{eq:16}
  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^{*} - \bar X_n)
  = \sum_{j=1}^{J_n} \Zb
\end{equation}
and
\begin{equation}\label{eq:17}
  \Em^{*}g(\Zb,\dots,\Zb[k]) = \frac{1}{n^{k-j+1}}
  \sum_{\tau_1=0}^{n-1} \cdots \sum_{\tau_{k-j+1}=0}^{n-1}
  g(Z_n(\tau_1, M_{nj}),\dots,Z_n(\tau_{k-j+1}, M_{nk}))
\end{equation}
almost surely for any function $g$ and any $j \leq k$. Equation~\eqref{eq:17}
conditions on the lengths of each block, but averages over their
starting points.

@@

\begin{proof}[Proof of Lemma~\ref{L1}]
  To prove part 1, observe that, for any increasing positive sequence
  $x_n$ such that $x_n p_n \to \infty$,
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
  \end{equation*}
  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
  $x_n = n x$ for any positive number $x$.  Then
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
    \lim \exp(-C n p_n e^{-n p_n x}) =
    \exp(0) = 1.
  \end{equation*}
  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.

@@

\begin{lem}\label{L6}
  Under the conditions of Theorem~\ref{T1},
  \begin{multline}\label{eq:30}
    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
    \E\Big(\max_{m = 1,\dots,m'} (n \, Z^*_n(\tau, m)^2 / m') \\
    \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
    = 0.
  \end{multline}
  Moreover, the families of random variables
  $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ and
  $\{\max_{m=1,\dots,M_{nj}} Z^{*}_{nj}(u_{nj}, m)^2 n / M_{nj}; j, n\}$ are uniformly integrable.
\end{lem}

\begin{proof}
  We will only present a proof of~\eqref{eq:30}. Uniform integrability
  of the first family of random variables is simply a restatement of
  that expression and uniform integrability of $Z_{nj}^{*2} n / M_{nj}$
  follows an abbreviated version of the proof of~\eqref{eq:30}.

  First we will show that, for every $\epsilon > 0$ and large enough
  $n$, there exists an $\epsilon' > 0$ with the property that
  \begin{equation}\label{eq:31}
    \E \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
  \end{equation}
  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn})$ with
  $\pr(A) \leq \epsilon'$. Then we will show that this property
  implies uniform integrability.\footnote{%
    The novelty in this part of the proof is the measurability
    requirement. The sigma-field $\Fs_n$ intentionally excludes the
    random variables that define the bootstrap (block length and block
    start periods) and any $A \in \Fs_n$ is independent of those
    variables, so $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measurable. If
    $\Fs_n$ were enlarged to include those variables then uniform
    integrability would be an immediate consequence of~\eqref{eq:31}
    and would not need to be shown separately. See \citet[Theorem
    12.9]{Dav:94}.} %

  Take an arbitrary $\delta > 0$ and a value of $\delta' > 0$
  so that
  \begin{equation}\label{eq:35}
    \sup_{m'=1,\dots,n} \E \Big(\ind(A) \max_{m = 1,\dots,m'}
    Z_n'(\tau, m)^2 n / m' \Big) < \delta
  \end{equation}
  for any $A \in \Fs_n$ with $\pr(A) \leq \delta'$; the existence
  of $\delta'$ is ensured by Lemma~\ref{L8}. For any $x$,
  define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$
  into a summation of conditionally independent blocks
  \begin{equation*}
  Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
  \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}),
  \end{equation*}
  giving
  \begin{align}
  \E  \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big)
  \notag \\
  &\leq 3 \E\Big[ \Em^{*} \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big]
  \notag \\
  &\quad + 3 \Em^{*} \big[\ind(A) \tfrac{n}{m'}
  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big]\Big]\label{eq:6}
  \end{align}
  almost surely.

  Since $Z_{nj}^*$ is a martingale difference array, Doob's maximal
  inequality for martingales \citep[see][Theorem 15.15, for
  example]{Dav:94} along with the construction of $Z_{nj}^{*}$ gives
  a bound for the first term on the \allcaps{RHS} of~\eqref{eq:6},
  \begin{align*}
  \E \Em^* & \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau)
  + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big] \\
  &\leq \tfrac{1}{m'} \sum_{u = 0}^{n-1} \E \Big[\Em \big[
  \ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2\big]\Big] \\
  &\leq \tfrac{3}{m'} \sum_{u = 0}^{n-1} \E\Big[\Em\big[
  \ind(A) Z'_n(u, K_{n,J(\tau)} - \tau)^2\big]
  + \tfrac{1}{n} \Pm[A] \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
  (\mu_{nt} - \bar \mu_n)\Big)^2 \\
  & \quad+ \sum_{j=J(\tau)+1}^{J(\tau + m')-1}
  \Em \big[\ind(A) Z_n'(u, M_{nj})^2]
  + \tfrac{1}{n} \Pm[A]
  \sum_{j=J(\tau)+1}^{J(\tau + m')-1}\Big( \sum_{t \in I_n(u,M_{nj})}
  (\mu_{nt} - \bar{\mu}_n) \Big)^2 \\
  & \quad+ \Em\big( \ind(A) Z_n'(u, n)^2 \big)
  \sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big] \\
  &\leq (3\delta/m') \E (K_{n,J(\tau+m')-1} - \tau)
    + 3\delta \E\Big(\sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big) \\
  &\quad+ \tfrac{3\delta'}{nm'} \sum_{u=0}^{n-1}\E\Big( \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
  (\mu_{nt} - \bar \mu_n)\Big)^2 +
  \sum_{j=J(\tau)+1}^{J(\tau + m')-1}\Big( \sum_{t \in I_n(u,M_{nj})}
  (\mu_{nt} - \bar{\mu}_n) \Big)^2 \Big) \\
  & < C_1 \delta + C_2 p_n \delta'
  \end{align*}
  for some finite constants $C_1$ and $C_2$.
  The second inequality comes from writing
  \begin{align*}
    Z_n(\tau, m) &= Z_n'(\tau, m)
    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)}
    \big((\mu_{nt} - \bar \mu_n) + (\bar \mu_n - \bar X_n)\big) \\
    &= Z_n'(\tau, m)
    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
    - (m/n) Z'_n(\tau, n),
  \end{align*}
  the third follows by construction of $A$
  and the fourth follows from an argument similar to Lemma~\ref{L3}.

  For the second term on the \allcaps{RHS} of~\eqref{eq:6}, use the
  sequence of inequalities
  \begin{align*}
  \E \Em^* \big[\ind(A) &\tfrac{n}{m'}
  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big] \\
  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')-1} \tfrac{n}{m'} \Em^* \big[\ind(A)
  \max_{m=1,\dots, \min(M_{nj}, m' - K_{n,j-1})} Z_n^*(K_{n,j}, m)^2 \big]\Big) \\
  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{1}{m'} \sum_{u=0}^{n-1} \Em \big[\ind(A)
  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n(u, m)^2 \big]\Big) \\
  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{3}{m'} \sum_{u=0}^{n-1} \Big\{
  \Em \big[\ind(A)
  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n'(u, m)^2 \big] \\
  &\quad +
  \tfrac{1}{n} \Pm[A] \max_{m = 1,\dots,\min(M_{nj}, m'-K_{n,j-1})}
  \Big(\sum_{t \in I_n(u,m)} (\mu_{nt} - \bar{\mu}_n)\Big)^2 \\
  &\quad+ \tfrac{\min(M_{nj},m'-K_{n,j-1})^2}{n^2} \Em( \ind(A) Z_n'(u, n)^2 ) \Big\}\Big)\\
  &\leq C'_1 \delta + C_2' \delta' p_n
  \end{align*}
  for constants $C_1'$ and $C_2'$. To express these bounds in the form
  of~\eqref{eq:31}, let $\epsilon > 0$ be arbitrary, choose $\delta'$
  such that~\eqref{eq:35} holds for $\delta = \epsilon/(2C_1+2C_1')$,
  and let $\epsilon' = \min(\delta', \epsilon/(2 C_2 + 2C_2'))$.
  A similar argument also
  implies that $n Z_n^*(\tau, m)^2 / m'$ has finite first moment.

  Now, for uniform integrability, take $\epsilon > 0$, choose
  $\epsilon'$ so that~\eqref{eq:31} holds for all $A \in \Fs_n$
  s.t. $\pr(A) \leq \epsilon'$, and choose $C_0$ large enough that
  \begin{equation*}
    \Pr\Big[ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C_0 \Big] \leq \epsilon'.
  \end{equation*}
  Markov's inequality guarantees the existence of this $C_0$. Then
  \begin{equation*}
    \E \Big(\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'
    \times \ind\Big\{ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C \Big\}\Big) \leq \epsilon
  \end{equation*}
  for all $C > C_0$. Since $\epsilon$ is arbitrary, this completes the proof.
\end{proof}

>>>>

By construction, (see Equations~\eqref{eq:39} and~\eqref{eq:1})
\begin{equation}\label{eq:16}
  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^{*} - \bar X_n)
  = \sum_{j=1}^{J_n} \Zb
\end{equation}
and
\begin{equation}\label{eq:17}
  \Em^{*}g(\Zb,\dots,\Zb[k]) = \frac{1}{n^{k-j+1}}
  \sum_{\tau_1=0}^{n-1} \cdots \sum_{\tau_{k-j+1}=0}^{n-1}
  g(Z_n(\tau_1, M_{nj}),\dots,Z_n(\tau_{k-j+1}, M_{nk}))
\end{equation}
almost surely for any function $g$ such that both
expressions are well-defined and any $j \leq k$. Equation~\eqref{eq:17}
conditions on the lengths of each block, but averages over their
starting points.

@@

\begin{proof}[Proof of Lemma~\ref{L1}]
  To prove part 1, take any positive number $x$. Then
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
    = (1 - (1 - p_n)^{n x})^{\lfloor C n p_n \rfloor}
    = \exp(-C n p_n e^{-x n p_n}) \times (1 + o(1))
  \end{equation*}
  since $(1 - p_n)^{x/p_n} \to e^{-x}$. In addition, $n p_n e^{-n p_n} \to 0$
  by assumption, so
  \begin{align*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
    \to \exp(0) = 1.
  \end{align*}
  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.

@@

\begin{lem}\label{L6}
  Under the conditions of Theorem~\ref{T1}, for any positive
  $\epsilon$ and $\epsilon'$ there exist constants $C_0$ and $n_0$
  such that
  \begin{multline}\label{eq:30}
    \pr \Big [ \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
    \Em \Big ( \max_{ m = 1, \dots, m' } (n \, Z^*_n(\tau, m)^2 / m' ) \\
    \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
    > \epsilon \Big ] < \epsilon'
  \end{multline}
  for all $n > n_0$ and $C > C_0$.
  Moreover, the families of random variables \\
  $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ and
  $\{Z^{*2}_{nj} n / M_{nj}; \tau, j, n\}$ are
  uniformly integrable for $n$ larger than some threshold $n_0$.
\end{lem}

\begin{proof}
  We will only present a proof of~\eqref{eq:30}.  Uniform
  integrability of $Z^{*2}_{nj} \, n / M_{nj}$ and
  $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$
  follow essentially the same arguments, replacing the conditional
  with the unconditional expectation, and are omitted.

  For any $x$, define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$
  into a summation of conditionally independent blocks, giving
  \begin{multline} \label{eq:42}
    Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
    \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* \\
    + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}).
  \end{multline}
  Since the distribution of $Z_n^*(\tau, m)$ does not depend on
  $\tau$, \eqref{eq:30} holds if, for any positive $\epsilon$ and
  $\epsilon'$, there exist $n_0$ and $C_0$ such that
  \begin{multline} \label{eq:31}
    \Pr \big [ \max_{\tau=0,\dots,n-1}
    \Em \big ( ( \max_{ m = 1, \dots, K_{n,J(\tau)} - \tau} n \, Z^*_n(\tau, m)^2 / M_{n,J(\tau)} ) \\
    \times \ind \{ \max_{ m = 1, \dots, K_{n,J(\tau)} - \tau} n \, Z^*_n(\tau, m)^2 / M_{n,J(\tau)} > C \}
    \big ) > \epsilon \big ] < \epsilon',
  \end{multline}
  \begin{multline} \label{eq:44}
    \pr \Big [
    \max_{m'=1,\dots,n}
    \Em \Big (
    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big\lvert \sum_{j=1}^{k} Z_{nj}^* \Big\rvert^2 \\
    \times \ind \Big \{
    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big\lvert \sum_{j=1}^{k} Z_{nj}^* \Big\rvert^2
    > C \Big \} \Big ) > \epsilon \Big ] < \epsilon'
  \end{multline}
  and
  \begin{multline} \label{eq:5}
    \Pr \big [ \max_{j=1,\dots,J_n}
    \Em \big ( ( \max_{ m = 1, \dots, M_{nj}} n \, Z^*_n(K_{n,j-1}, m)^2 / M_{nj} ) \\
    \times \ind \{ \max_{ m = 1, \dots, M_{nj}} n \, Z^*_n(K_{n,j-1}, m)^2 / M_{nj} > C \}
    \big ) > \epsilon \big ] < \epsilon',
  \end{multline}
  for all $n > n_0$ and $C > C_0$.

  For~\eqref{eq:5}, use the equality
  \begin{equation}
    Z_n(\tau, m) = Z_n'(\tau, m)
    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
    - (m/n) Z'_n(\tau, n), \label{eq:35}
  \end{equation}
  to get the upper bound
  \begin{align*}
    \Em \big ( & ( \max_{ m = 1, \dots, M_{nj} } n \, Z^*_n(K_{n,j-1},m)^2 / M_{nj} )
    \ind \{ \max_{ m = 1, \dots, M_{nj} } n \, Z^*_n(K_{n,j-1}, m) ^2 / M_{nj} > C \} \big ) \\
    & \leq 3 \Em \big ( ( \max_{ m = 1, \dots, M_{nj} } n \, Z'_n(u_n,m)^2 / M_{nj} )
    \ind \{ \max_{ m = 1, \dots, M_{nj} } n \, Z'_n(u_n,m)^2 / M_{nj} > C / 3 \} \big ) \\
    & \quad + 3 \Em \big ( ( M_{nj} Z'_n(0,n)^2 / n )
    \ind \{ M_{nj} Z'_n(0,n)^2 / n > C / 3 \} \big )
    + 3 \tfrac{M_{nj}}{n} \sum_{t=1}^n ( \mu_{nt} - \bar \mu_n ) ^2,
  \end{align*}
  where $u_n$ has the discrete uniform distribution over $0,\dots,n-1$.
  Lemmas~\ref{L1}, \ref{L3}, and \ref{L8} ensure that there exist
  $n_0$ and $C_0$ such that, for all $n > n_0$ and $C > C_0$,
  \begin{equation*}
    \Em \big ( (\max_{ m = 1, \dots, M_{nj} } n \, Z'_n(u_n,m)^2 / M_{nj} )
    \ind \{\max_{ m = 1, \dots, M_{nj} } n \, Z'_n(u_n,m)^2 / M_{nj} > C / 3 \}
    \big ) < \epsilon / 9
  \end{equation*}
  and
  \begin{equation*}
    \Em \big ( ( M_{nj} \, Z'_n(0,n)^2 / n )
    \ind \{ M_{nj} \, Z'_n(0,n)^2 / n > C / 3 \} \big )
    < \epsilon / 9
  \end{equation*}
  for all $j = 1,\dots,J_n - 1$ almost surely, and
  \begin{equation*}
    \pr \Big [ \max_{j=1,\dots,J_n-1}
    \tfrac{M_{nj}}{n} \sum_{t=1}^n ( \mu_{nt} - \bar \mu_n )^2 > \epsilon / 9 \Big ]
    < \epsilon' / 3,
  \end{equation*}
  proving~\eqref{eq:5}. The proof of~\eqref{eq:31} is essentially the same.

  The proof of~\eqref{eq:44} follows a streamlined version of \citet[Lemma
  6.5]{Mcl:75b} and \citet[Lemma 3.5]{Mcl:77}. (Those results are
  presented as Theorem~16.13 in \citealp{Dav:94}, and are largely
  reproduced in the proof of this paper's Lemma~\ref{L8}.)

  Separate $Z_{nj}^*$ into two components,
  \begin{align*}
    U_{nj}^* &= (\tfrac{n}{m'})^{1/2} \, Z_{nj}^*
    \ind\{\tfrac{n}{M_{nj}} \, Z_{nj}^{*2} > C' \} -
    (\tfrac{n}{m'})^{1/2} \Em^*( Z_{nj}^*
    \ind\{\tfrac{n}{M_{nj}} Z_{nj}^{*2} > C' \}) \\
    Y_{nj}^* &= (\tfrac{n}{m'})^{1/2} \, Z_{nj}^*
    \ind\{\tfrac{n}{M_{nj}} \, Z_{nj}^{*2} \leq C' \} -
    (\tfrac{n}{m'})^{1/2} \Em^*( Z_{nj}^*
    \ind\{\tfrac{n}{M_{nj}} Z_{nj}^{*2} \leq C'\}),
    \intertext{making}
    Z_{nj}^* &= (\tfrac{m'}{n})^{1/2} U_{nj}^* + (\tfrac{m'}{n})^{1/2} Y_{nj}^*
  \end{align*}
  where $C'$ is a constant that will be constrained later in the
  proof. For any $C$, $\tau$, $m'$, and $n$, standard probabilistic
  inequalities~(e.g. Theorem 2.29 of \citealp{Dav:94}, along with
  maximal inequalities for martingale difference sequences) imply that
  \begin{multline}
    \Em \Big ( \tfrac{n}{m'} \max_{k=1,\dots,J(m')}
    \Big \lvert \sum_{j=1}^{k} Z_{nj}^* \Big \rvert^2 \ind \Big \{
    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big \lvert \sum_{j=1}^{k}
    Z_{nj}^* \Big \rvert^2 > C \Big \} \Big ) \leq \\
    \tfrac{6}{C} \tfrac{4^4}{3^4}
    \Em \Big \lvert \sum_{j=1}^{J(m')} Y_{nj}^* \Big \rvert^4
    + 24 \Em \Big \lvert \sum_{j=1}^{J(m')} U_{nj}^* \Big \rvert^2
    \label{eq:43}
  \end{multline}
  almost surely.

  The first term on the RHS of~\eqref{eq:43} can be
  expanded recursively to give the following upper bound
  \begin{align*}
    \tfrac{1}{C} \Em \Big\lvert \sum_{j=1}^{J(m')} Y_{nj}^* \Big\rvert^4
    & \leq \Em \Big[ \tfrac{1}{C} \Em^* \Big\lvert \sum_{j=1}^{J(m')-1} Y_{nj}^* \Big\rvert^4
    + \tfrac{6}{C} \Em^* \Big( Y_{n,J(m')}^{*2} \Big\lvert
    \sum_{j=1}^{J(m')-1} Y_{nj}^* \Big\rvert^2 \Big) \\
    & \quad + \tfrac{4}{C} \Em^* \Big\lvert Y_{n,J(m')}^{*3} \sum_{j=1}^{J(m')-1} Y_{nj}^* \Big\rvert
    + \tfrac{1}{C} \Em^* \lvert Y_{n,J(m')}^{*4} \rvert \Big] \\
    & \leq \tfrac{1}{C} \Em^* \Big ( \sum_{j=1}^{J(m')-1} Y_{nj}^* \Big ) ^4
    + \tfrac{1}{C} (\tfrac{4 C'}{m'})^2
    \Big( 6 M_{n,J(m')} \sum_{j=1}^{J(m')-1} M_{nj} \\
    & \quad + 4 M_{n,J(m')}^{3/2} \Big [ \sum_{j=1}^{J(m')-1} M_{n,J(m')} \Big ] ^{1/2}
    + M_{n,J(m')}^2 \Big ) \\
    & \leq \tfrac{ 1 }{ C } ( \tfrac{ 4 C' }{ m' } )^2 \sum_{j=2}^{J(m')}
      \Big ( 6 M_{nj} \sum_{ k = 1 }^{ j - 1 } M_{nk}
      + 4 M_{nj}^{3/2} \Big [ \sum_{ k = 1 }^{ j - 1 } M_{ nk } \Big ] ^{1/2}
      + M_{nj}^2 \Big ) \\
    & \leq \tfrac{11}{C} \tfrac{ K _{ n, J(m') } }{ m' } (4 C')^2
  \end{align*}
  with all inequalities holding almost surely.
  The second to last inequality holds by recursively applying the previous
  two inequalities, first for $J(m')-1$, then for $J(m')-2$, etc.

  The second term on the RHS of~\eqref{eq:43} satisfies
  \begin{align*}
    \Em \Big \lvert \sum_{j=1}^{J(m')} U_{nj}^* \Big \rvert^2
    & = \sum_{j=1}^{J(m')} \Em \lvert U_{nj}^* \rvert^2 \\
    & \leq \max_{j=1,\dots,J(m')} \Em \big(
      \tfrac{n}{M_{nj}} Z_{nj}^{*2}
      \ind\{ \tfrac{n}{M_{nj}} Z_{nj}^{*2} > C' \} \big) .
  \end{align*}
  Equation~\eqref{eq:5} ensures that we can choose $C'$ and $n'$ such that
  \begin{equation*}
    \pr \Big [
    \max_{j=1,\dots,J(m')} \Em \big(
      \tfrac{n}{M_{nj}} Z_{nj}^{*2}
      \ind\{ \tfrac{n}{M_{nj}} Z_{nj}^{*2} > C \} > \epsilon / 2 \big) \Big ]
    < \epsilon' / 2
  \end{equation*}
  for all $n > n'$ and $C > C'$. We can then choose $n_0 > n'$ and $C_0 > C'$
  such that
  \begin{equation*}
    \pr \Big [
    \max_{ m' = 1, \dots, n }
    \tfrac{11}{C} \tfrac{ K _{ n, J(m') } }{ m' } (4 C')^2
    > \epsilon / 2 \Big ] < \epsilon' / 2
  \end{equation*}
  for all $n > n_0$ and $C > C_0$,
  completing the proof.
\end{proof}
